%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Jonathan Bluhm} \\ \vspace{1pt}
    Westminster, Colorado \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 719-243-9318 ~ \href{mailto:bluhmjc@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{bluhmjc@gmail.com}} ~ 
    \href{https://github.com/johnnybluhm}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/johnnybluhm}} ~
    \vspace{-8pt}
\end{center}

%-------------SUMMARY---------------%

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, Java, Python, Typescript, Javascript, C, SQL, Bash, HTML, CSS} \\
     \textbf{Technologies}{: Linux, Windows, Asp.net Core, Node.js, Msbuild, Docker, Gitlab CI, Azure Devops, Splunk, Powershell} \\
     \textbf{Other}{: Data Structures and Algorithms, Agile, Unit Testing, Code Reviews, REST, Microservices, Distributed Systems} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  	\resumeSubheading
      {Geico}{2023 -- Present}
      {Engineer II}{Remote}
      \resumeItemListStart
        \resumeItem{Collaborated with various engineering teams across Geico to deliver a new, streamlined commercial auto insurance experience. This new experience cuts down the time for customers to get a quote by 50\%.}
        \resumeItem{Updated systems to allow drivers with suspended licenses to get a quote. This new feature could generate up to \$150,000 a year in revenue for Geico.}
        \resumeItem{Assisted in the development of a new Independent Agent commercial insurance product. This product leveraged legacy systems to create a new web experience for insurance agents. The new web experience will save agents hours each day when creating certain quotes.}
      \resumeItemListEnd

    \resumeSubheading
      {Sphere Commerce}{2022 -- 2023}
      {Software Engineer}{Westminster, Colorado}
      \resumeItemListStart
        \resumeItem{Worked with a team of six engineers to improve the stability of the integrated payment application. The integrated payment application is a multithreaded, microservice architecture, cloud based application that processes payments for thousands of clients across the United States.}
        \resumeItem{Cleaned up unnecessary logs made by our logging service, reducing the amount of data logged to splunk every day from 200GB to 10GB.}
        \resumeItem{Identified and corrected a memory leak in a long running process. The fix allowed us to change the machine it was running on from an i2 to an i1 instance, saving around \$300/month.}
        \resumeItem{Fixed unit tests that would periodically fail. Due to the multithreaded nature of the integrated payment application, certain unit tests would fail due to timing issues. Many of these were fixed, leading to far quicker builds and easier development.}
      \resumeItemListEnd

    \resumeSubheading
      {Dish Network}{2021 -- 2022}
      {Software Engineer I}{Superior, Colorado}
      \resumeItemListStart
        \resumeItem{Worked closely with eight other engineers to design, develop, deploy, and maintain software applications for the Dish Network uplink center. These applications allow internal teams to monitor over 6000 TV channels in real-time and automate workflows.}
        \resumeItem{Upgraded six year old website to use modern web development tools. The older website had no modules and tests, so I integrated node.js into the project to allow for dependency management and testing. Developers can now easily modify and expand the website and be confident of their changes.}
        \resumeItem{Handled on-call issues from stakeholders, saving the company money by minimizing downtime of our applications.}
        \resumeItem{Mentored new team members, allowing them to contribute to projects with confidence.}
    \resumeItemListEnd

    \resumeSubheading
      {United States Navy}{2013 -- 2017}
      {Nuclear Electrician}{Groton, Connecticut}
      \resumeItemListStart
        \resumeItem{Functioned as an integral part within a watch team to maintain smooth operation of the reactor plant during complex evolutions.}
        \resumeItem{Solved problems efficiently by referencing manuals and textbooks.}
        \resumeItem{Retained the vital documentation for maintenance and history of the reactor control system.}
        \resumeItem{Communicated effectively with peers from a wide variety of disciplines and backgrounds.}        
    \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Colorado Boulder}{2019 -- 2021}
      {Bachelor of Science in Computer Science}{Boulder, Colorado}
      \resumeItemListStart
        \resumeItem{GPA: 3.76}
        \resumeItem{Course Work: Linux System Admin, Network Systems, Operating Systems, Robotics, Algorithms, Human Computer Interaction, Data Structures, Cybersecurity, Machine Learning, Calculus 1-3, Probability and Statistics, Linear Algebra}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}
